A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-07 paper.tex
Add solidity codes to Chap5

The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract. As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and written on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product}. Finally, data providers can start uploading data.

@@

@@

Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to public. Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process. The key sending process is shown in Fig.~\ref{fig:key_exchange}. The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.

@@

>>>>

The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract. As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and written on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}. Finally, the data product is launched and data providers can start uploading data.

@@

\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
	function addHashedKey(
		string memory _hashedKey
	) public {
		require(
			msg.sender == provider,
			"Only provider can add hashed key."
		);
		require(
			state == State.Launched,
			"One key has been certified."
		);
		hashedKey = hashedKey;
		emit newHashedKey(hashedKey);
	}

	function addCertifiedKey(
		string memory _certifiedKey
	) public {
		require(
			msg.sender == broker,
			"Only broker can add certifiedKey."
		);
		require(
			state == State.Launched,
			"One key has been certified."
		);
		certifiedKey = _certifiedKey;
		state = State.KeyCertified;
		emit newCertifiedKey(certifiedKey);
	}
\end{lstlisting}

@@

Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to public. Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process. The key sending process is shown in Fig.~\ref{fig:key_exchange} and Listing.~\ref{lst:key_exchange}. The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.

@@

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}

\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
    function addEncryptKey(
        address _consumer,
        string memory _encryptKey
    ) public {
        require(
            msg.sender == provider,
            "Only provider can add the encrypted key."
        );
        require(
            consumer2Purchase[_consumer].isKeyAdded == false,
            "Encryption key has been added."
        );
        consumer2Purchase[_consumer].encryptKey = _encryptKey;
        consumer2Purchase[_consumer].isKeyAdded = true;
        emit newEncryptKey(_consumer, _encryptKey);
    }
\end{lstlisting}
